---
title: "Cross Validation"
output: github_document
---

```{r setup,include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp =0.6,
  out.width = "90%"
) 

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(1)
```

## Simulate the data

runif (number,lower bound, upper bound)

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

```
Look at the data 

```{r}

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

## Cross validation by hand
Get training and test dataset
80/20 rule
anti_join(df,not exist here)
by --arrange by id
```{r}
train_df = sample_n(nonlin_df, size=80)
test_df = anti_join(nonlin_df, train_df, by = "id")


```

Fit three models

```{r}
linear_mod=lm(y~x,data=train_df)
smooth_mod=gam(y~s(x),data = train_df)
wiggly_mod=gam(y~s(x,k=30),sp=10e-6,data=train_df)
```


can i see what i just did
```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x=x,y=y))+
  geom_point()+ 
  geom_line(aes(y=pred),color="red")
```

```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x=x,y=y))+
  geom_point()+ 
  geom_line(aes(y=pred),color="red")
```


```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x=x,y=y))+
  geom_point()+ 
  geom_line(aes(y=pred),color="red")
```


Test three models at same time 
```{r}
train_df %>% 
  gather_predictions(linear_mod,smooth_mod,wiggly_mod) %>% 
  ggplot(aes(x=x,y=y))+
  geom_point()+ 
  geom_line(aes(y=pred),color="red") +
  facet_grid(.~model)
```

look at prediction accuracy.
```{r}
rmse(linear_mod,test_df)
rmse(smooth_mod,test_df)
rmse(wiggly_mod,test_df)
```

## Criss validation using `modelr`
```{r}
cv_df=
  crossv_mc(nonlin_df,100)
```
waht is happening here..
crossv_mc preforms the training / testing split multiple times..
```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as.tibble()
cv_df %>% pull(test) %>% .[[1]] %>% as.tibble()
```

```{r}
cv_df =cv_df %>% 
  mutate(train=map(train,as_tibble),
         test=map(test,as_tibble))
```
Let's try to fit models and get RMSEs for them
.x is new varibale name--data from train
map2 map across 2 variables
```{r}
cv_df=cv_df %>% 
  mutate(linear_mod = map(.x=train,~lm(y~x,data=.x )),
         smooth_mod=map(.x=train,~gam(y~s(x),data=.x )),
         wiggly_mod=map(.x=train,~gam(y~s(x,k=30),sp=10e-6,data=.x ))) %>% 
  mutate(
    rmse_linear=map2_dbl(.x=linear_mod,.y=test, ~rmse(model=.x,data=.y)),
    rmse_smooth=map2_dbl(.x=smooth_mod,.y=test, ~rmse(model=.x,data=.y)),                       rmse_wiggly=map2_dbl(.x=wiggly_mod,.y=test, ~rmse(model=.x,data=.y)))
```

what do these results say about the model choice?
fct_inorder(): by the order in which they first appear.
fct_infreq(): by number of observations with each level (largest first)
 names_prefix =remove the rmse
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

group_by=control
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
    group_by(model) %>% 
    summarize(avg_rmse=mean(rmse))
```

## Try on a real dataset

import my data 
```{r}
child_growth = read_csv("./nepalese_children.csv") %>% 
   mutate(weight_cp = (weight > 7) * (weight - 7))
```

weight vs arm circumference
```{r}
child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```

```{r}
linear_mod = lm(armc ~ weight, data = child_growth)
pwlin_mod  = lm(armc ~ weight + weight_cp, data = child_growth)
smooth_mod = gam(armc ~ s(weight), data = child_growth)
```

```{r}
child_growth %>% 
     gather_predictions(linear_mod,pwlin_mod,smooth_mod) %>% 
    ggplot(aes(x=weight,y=armc))+
    geom_point(alpha=0.3)+ 
    geom_line(aes(y=pred),color="red") +
    facet_grid(.~model)
```
try to understand model fit by using CV
```{r}
cv_df =
  crossv_mc(child_growth, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_mod  = map(train, ~lm(armc ~ weight, data = .x)),
    pwl_mod     = map(train, ~lm(armc ~ weight + weight_cp, data = .x)),
    smooth_mod  = map(train, ~gam(armc ~ s(weight), data = as_tibble(.x)))) %>% 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_pwl    = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)))
```

pwlin is the best-not huge improvement from pwlin to smooth and huge improvement from linear
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

